Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-14 ijar-npb-ms.tex
tweaking some of Louis' language edits of sec 4

As a simple example, imagine that we expect $\ptk$ to be about $0.75$ for a certain $k$ and $t$,
so we choose $\yktz = 0.75$,
and that we value this choice of mean functioning probability with $\nktz = 8$,
i.e., equivalently to having seen $8$ observations with a mean $0.75$.
If we observe $n_k = 16$ components of type $k$ in the test data and $s^k_t = 12$ function at time $t$,
then $s^k_t/n_k = 0.75$ as we expect,
so that the updated parameters are $\nktn = 24, \yktn=0.75$.
However, in contrast, unexpectedly observing that no component functions at time $t$ instead
leads to parameters $\nktn = 24, \yktn=0.25$.
The prior and the posteriors based on these two scenarios
are depicted in Figure~\ref{fig:singleprior-pdc}
%through their Beta densities and cdfs (left)
%and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$ and cmfs
for the case $m_k = 5$ (right).

@@

\begin{figure}
\includegraphics[width=\textwidth]{singleprior-pdc2}
\caption{Beta densities (top left) and cdfs (bottom left),
with the corresponding Beta-binomial posterior predictive probability mass functions (top right) and cumulative mass functions (bottom right),
for a prior with $\nktz = 8, \yktz = 0.75$,
and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior~1) and $s^k_t=0$ (Posterior~2), respectively.
Data for Posterior~1 confirm prior assumptions,
while data for Posterior~2 are in conflict with the prior.
However, this conflict is averaged out,
and Posterior 1 and Posterior 2 have the same spread, both in the posterior pdf/cdf and the posterior predictive pmf/cmf,
such that Posterior 2 gives a false sense of certainty despite the massive conflict between prior and data.}
\label{fig:singleprior-pdc}
\end{figure}

>>>>

As a simple example, imagine that we expect $\ptk$ to be about $0.75$ for a certain $k$ and $t$,
so we choose $\yktz = 0.75$,
and that we value this choice of mean functioning probability with $\nktz = 8$,
i.e., equivalently to having seen $8$ observations with a mean $0.75$.
If we observe $n_k = 16$ components of type $k$ in the test data and $s^k_t = 12$ function at time $t$,
then $s^k_t/n_k = 0.75$ as we expect,
so that the updated parameters are $\nktn = 24, \yktn=0.75$.
However, in contrast, unexpectedly observing that no component functions at time $t$ instead
leads to parameters $\nktn = 24, \yktn=0.25$.
The prior and the posteriors based on these two scenarios
are depicted in the left panels of Figure~\ref{fig:singleprior-pdc},
%through their Beta densities and cdfs (left)
%and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$ and cmfs
along with their corresponding predictive Beta-binomial pmf and cmf
for the case $m_k = 5$ (right panels).

@@

\begin{figure}
\includegraphics[width=\textwidth]{singleprior-pdc2}
\caption{Beta densities (top left) and cdfs (bottom left),
with the corresponding Beta-binomial predictive probability mass functions (top right) and cumulative mass functions (bottom right),
for a prior with $\nktz = 8, \yktz = 0.75$,
and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior~1) and $s^k_t=0$ (Posterior~2), respectively.
Data for Posterior~1 confirm prior assumptions,
while data for Posterior~2 are in conflict with the prior.
However, this conflict is averaged out,
and Posterior 1 and Posterior 2 have the same spread, both in the posterior pdf/cdf and the posterior predictive pmf/cmf,
such that Posterior 2 gives a false sense of certainty despite the massive conflict between prior and data.}
\label{fig:singleprior-pdc}
\end{figure}
